---
title: "Data Preparation"
output: html_document
params:
  data: data
  fun_options: fun_options
---

```{r global_options, include=FALSE}
library(rmarkdown)

data <- params$data

opts <- params$fun_options
knitr::opts_chunk$set(fig.width = 14, fig.height = 10, echo = TRUE)
```

### General Information
This report is intended to help prepare your data. Additional fuctions for preparation are the following:

* p.numeric(dta): Lists numeric variables.
+ p.continuous(dta, max_levels): Lists numeric continuous variables. Default for max_levels is .1 which restricts to numeric variables with 10% or more unique values.
+ p.discrete(dta, max_levels): Lists numeric discrete variables. Default for max_levels is .1 which restricts to numeric variables with less than 10% unique values.
+ p.integer(dta): Lists integer variables.
+ p.character(dta): Lists character variables.
+ p.unique(dta): Lists variables where every value is unique.
+ p.factor(dta): Lists factor variables.
+ p.asFactor(dta, columns): Converts variables to factors. Default for columns is any numeric discrete variables.
+ p.replaceNull(dta, columns, null_value): Replaces null values for factor variables. The default null_value is "Missing". Good to use in combination with p.factor().
+ p.removeVariables(dta, columns): Removes variables from data set. Good to use in combination with p.unique().


#### Top row & bottom row sample of data 

```{r prep_TopBottom}
head(data)
tail(data)
```


#### Data Structure

```{r prep_Structure}
str(data)
```

#### Data Summary
Builds off of the describe() function.
```{r prep_Summary}
p.summary(data) #* represents factor variables.
```

#### Data Structure (Summary of Variables)
Numeric discrete lists any numeric variables where less than 10% of their data is unique.
```{r prep_DetailedStructure}
p.structure(data)
```

#### Table Summaries of Data
Table summary of all numeric discrete & factor variables with 100 or less distinct values. Builds off of the table() function. For a specific table summary of a variable use the table() function.
```{r prep_Table}
p.table(data)
```

#### Missing Data
The following graphs shows the distribution of missing values.
```{r prep_PlotNull}
DataExplorer::PlotMissing(data)
VIM::aggr(data, numbers=TRUE)
```

